% Copyright 2013 Christophe-Marie Duquesne <chmd@chmd.fr>
% Copyright 2014 Mark Szepieniec <http://github.com/mszep>
% 
% ConText style for making a resume with pandoc. Inspired by moderncv.
% 
% This CSS document is delivered to you under the CC BY-SA 3.0 License.
% https://creativecommons.org/licenses/by-sa/3.0/deed.en_US

\startmode[*mkii]
  \enableregime[utf-8]  
  \setupcolors[state=start]
\stopmode

\setupcolor[hex]
\definecolor[titlegrey][h=757575]
\definecolor[sectioncolor][h=397249]
\definecolor[rulecolor][h=9cb770]

% Enable hyperlinks
\setupinteraction[state=start, color=sectioncolor]

\setuppapersize [A4][A4]
\setuplayout    [width=middle, height=middle,
                 backspace=20mm, cutspace=0mm,
                 topspace=10mm, bottomspace=20mm,
                 header=0mm, footer=0mm]

%\setuppagenumbering[location={footer,center}]

\setupbodyfont[11pt, helvetica]

\setupwhitespace[medium]

\setupblackrules[width=31mm, color=rulecolor]

\setuphead[chapter]      [style=\tfd]
\setuphead[section]      [style=\tfd\bf, color=titlegrey, align=middle]
\setuphead[subsection]   [style=\tfb\bf, color=sectioncolor, align=right,
                          before={\leavevmode\blackrule\hspace}]
\setuphead[subsubsection][style=\bf]

\setuphead[chapter, section, subsection, subsubsection][number=no]

%\setupdescriptions[width=10mm]

\definedescription
  [description]
  [headstyle=bold, style=normal,
   location=hanging, width=18mm, distance=14mm, margin=0cm]

\setupitemize[autointro, packed]    % prevent orphan list intro
\setupitemize[indentnext=no]

\setupfloat[figure][default={here,nonumber}]
\setupfloat[table][default={here,nonumber}]

\setuptables[textwidth=max, HL=none]

\setupthinrules[width=15em] % width of horizontal rules

\setupdelimitedtext
  [blockquote]
  [before={\setupalign[middle]},
   indentnext=no,
  ]


\starttext

\section[guangchuang-yu]{Guangchuang Yu}

\thinrule

\placetable[none]{}
\starttable[|l|r|]
\HL
\NC School of Public Health, The University of Hong Kong
\NC (852)-62269693
\NC\AR
\NC L5-14, 5/F, Laboratory Block, Faculty of Medicine Building
\NC \useURL[url1][mailto:gcyu@connect.hku.hk][][gcyu@connect.hku.hk]\from[url1]
\NC\AR
\NC 21 Sassoon Road, Pokfulam, Hong Kong
\NC \useURL[url2][http://guangchuangyu.github.io]\from[url2]
\NC\AR
\HL
\stoptable

\thinrule

\subsection[education]{Education}

\startdescription{2013-2017 (expected)}
  {\bf PhD}; The University of Hong Kong; {\em Evolution Study of
  Influenza A Virus}
\stopdescription

\startdescription{2006-2009}
  {\bf MSc}; Anhui Medical University; {\em Biochemistry and Molecular
  Biology}
\stopdescription

\startdescription{2001-2005}
  {\bf BSc}; South China Agricultural University; {\em Biotechnology}
\stopdescription

\startdescription{2015}
  Institut Pasteur, Paris; {\em Train the Trainers 2015}
\stopdescription

\subsection[professional-experience]{Professional Experience}

\startdescription{2015}
  {\bf INDA Steering Committee}; International Network for Data
  Analysis, Institut Pasteur
\stopdescription

\startdescription{2009-2013}
  {\bf Bioinformatician}; College of Life Science and Technology, Jinan
  University
\stopdescription

\startdescription{2007-2009}
  {\bf Visiting Student}; Beijing Institute of Radiation Medicine
\stopdescription

\subsection[software-development]{Software Development}

\startitemize[packed]
\item
  \useURL[url3][https://github.com/GuangchuangYu/ChIPseeker][][ChIPseeker]\from[url3]:
  ChIP peak Annotation, Comparison and Visualization
\item
  \useURL[url4][https://github.com/GuangchuangYu/clusterProfiler][][clusterProfiler]\from[url4]:
  Comparing biological themes among gene clusters
\item
  \useURL[url5][https://github.com/GuangchuangYu/DOSE][][DOSE]\from[url5]:
  Disease Ontology Semantic and Enrichment analysis
\item
  \useURL[url6][https://github.com/GuangchuangYu/ggtree][][ggtree]\from[url6]:
  Phylogenetic tree viewer for different types of tree annotations
\item
  \useURL[url7][https://github.com/GuangchuangYu/GOSemSim][][GOSemSim]\from[url7]:
  GO-terms and gene samantic similarity measures
\item
  \useURL[url8][https://github.com/GuangchuangYu/ReactomePA][][ReactomePA]\from[url8]:
  Reactome pathway analysis
\stopitemize

\subsection[awards]{Awards}

\startitemize[packed]
\item
  2013-2017, Postgraduate Studentships (for PhD students at The
  University of Hong Kong)
\item
  2012, Best paper of the year 2010, Journal of Integrated OMICS.
\stopitemize

\subsection[grants]{Grants}

\startitemize[packed]
\item
  2013 (completed), PI, Investigate functions of hnRNPK in regulating
  cytokinesis of human lung cancer cell, Fundamental Research Funds for
  the Central Universities (21613414), ￥100,000
\item
  2011 (completed), PI, Dynamic proteomic analysis of HeLa cell cycle,
  Fundamental Research Funds for the Central Universities (21611303),
  ￥20,000
\stopitemize

\subsection[publications]{Publications}

\startblockquote
Citation = 435, H-index = 10, I10-index = 11
\stopblockquote

\startblockquote
(data from
\useURL[url9][https://scholar.google.com/citations?user=DO5oG40AAAAJ&hl=en][][Google
Scholar]\from[url9], Jan 2016)
\stopblockquote

\startitemize[n,packed][stopper=.,width=2.0em]
\item
  {\bf G Yu}, DK Smith, H Zhu, Y Guan, TTY Lam\high{*}. ggtree: an R
  package for visualization and annotation of phylogenetic tree with
  different types of meta-data. {\bf {\em Methods in Ecology and
  Evolution}}. Submitted.
\item
  {\bf G Yu}, QY He\high{*}.
  \useURL[url10][http://pubs.rsc.org/en/Content/ArticleLanding/2016/MB/C5MB00663E][][ReactomePA:
  an R/Bioconductor package for reactome pathway analysis and
  visualization]\from[url10]. {\bf {\em Molecular BioSystems}}. 2016,
  Accepted.
\item
  {\bf G Yu}\high{*}, LG Wang, QY He\high{*}.
  \useURL[url11][http://bioinformatics.oxfordjournals.org/cgi/content/abstract/btv145][][ChIPseeker:
  an R/Bioconductor package for ChIP peak annotation, comparision and
  visualization]\from[url11]. {\bf {\em Bioinformatics}}. 2015,
  31(14):2382-2383.
\item
  {\bf G Yu}\high{*}, LG Wang, GR Yan, QY He\high{*}.
  \useURL[url12][http://bioinformatics.oxfordjournals.org/cgi/content/abstract/btu684][][DOSE:
  an R/Bioconductor package for Disease Ontology Semantic and Enrichment
  analysis]\from[url12]. {\bf {\em Bioinformatics}}. 2015,
  31(4):608-609.
\item
  X Sun\high{†}, {\bf G Yu}\high{†}, Q Xu, N Li, C Xiao, X Yin, K Cao, J
  Han, QY He\high{*}.
  \useURL[url13][http://pubs.rsc.org/en/content/articlelanding/2013/mt/c3mt00126a][][Putative
  cobalt- and nickel-binding proteins and motifs in {\em Streptococcus
  pneumonia}]\from[url13]. {\bf {\em Metallomics}}. 2013, 5(7):928-935.
\item
  YY Zhu\high{†}, {\bf G Yu}\high{†}, Y Zhang, Z Xu, YQ Huang, GR
  Yan\high{*}, QY He\high{*}.
  \useURL[url14][http://onlinelibrary.wiley.com/doi/10.1002/pmic.201200273/abstract][][A
  novel andrographolide derivative AL-1 exerts its cytotoxicity on K562
  cells through a ROS-dependent mechanism]\from[url14].
  {\bf {\em Proteomics}}, 2013, 13(1):169-178.
\item
  {\bf G Yu}\high{†}, LG Wang\high{†}, XH Meng, QY He\high{*}.
  \useURL[url15][http://www.biomedcentral.com/1756-0500/5/360/][][LXtoo:
  an integrated live Linux distribution for the bioinformatics
  community]\from[url15]. {\bf {\em BMC Research Notes}}. 2012,
  5(1):360.
\item
  {\bf G Yu}, LG Wang, Y Han, QY He\high{*}.
  \useURL[url16][http://online.liebertpub.com/doi/abs/10.1089/omi.2011.0118][][clusterProfiler:
  an R package for comparing biological themes among gene
  clusters]\from[url16]. {\bf {\em OMICS: A Journal of Integrative
  Biology}}. 2012, 16(5):284-287.
\item
  {\bf G Yu}, QY He\high{*}.
  \useURL[url17][http://www.jclinbioinformatics.com/content/1/1/15/abstract][][Functional
  similarity analysis of human virus-encoded miRNAs]\from[url17].
  {\bf {\em Journal of Clinical Bioinformatics}}. 2011, 1(1):15.
\item
  {\bf G Yu}\high{†}, CL Xiao\high{†}, X Bo, CH Lu, Y Qin, S Zhan, QY
  He\high{*}.
  \useURL[url18][http://www.jiomics.com/index.php/jio/article/view/21][][A
  new method for measuring functional similarity of
  microRNAs]\from[url18]. {\bf {\em Journal of Integrated OMICS}}. 2011,
  1(1):49-54.
\item
  {\bf G Yu}\high{†}, CL Xiao\high{†}, CH Lu\high{†}, HT Jia, F Ge, W
  Wang, XF Yin, HL Jia, JX He\high{*}, QY He\high{*}.
  \useURL[url19][http://pubs.rsc.org/en/Content/ArticleLanding/2011/MB/C0MB00055H][][Phosphoproteome
  profile of human lung cancer cell line A549]\from[url19].
  {\bf {\em Molecular BioSystems}}. 2011, 7(2):472-479.
\item
  {\bf G Yu}\high{†}, F Li\high{†}, Y Qin, X Bo\high{*}, Y Wu, S
  Wang\high{*}.
  \useURL[url20][http://bioinformatics.oxfordjournals.org/cgi/content/abstract/26/7/976][][GOSemSim:
  an R package for measuring semantic similarity among GO terms and gene
  products]\from[url20]. {\bf {\em Bioinformatics}}. 2010,
  26(7):976-978.
\item
  XY Yang, K He, G Du, X Wu, {\bf G Yu}, Y Pan, G Zhang, X Sun, QY He.
  Integrated Translatomics with Proteomics to Identify Novel
  Iron--Transporting Proteins in {\em Streptococcus pneumoniae}.
  {\bf {\em Frontiers Microbiology}}. 2016, Accepted
\item
  PY Huang, CCD Lee, CH Yip, CL Cheung, {\bf G Yu}, TTY Lam, DK Smith, H
  Zhu\high{*}, Y Guan\high{*}.
  \useURL[url21][http://www.sciencedirect.com/science/article/pii/S1567134815300721][][Genetic
  characterization of highly pathogenic H5 influenza viruses from
  poultry in Taiwan, 2015]\from[url21]. {\bf {\em Infection, Genetics
  and Evolution}}. 2016, 38:96-100.
\item
  SH Xu, JZ Huang, ML Xu, {\bf G Yu}, XF Yin, D Chen\high{*}, GR
  Yan\high{*}.
  \useURL[url22][http://onlinelibrary.wiley.com/doi/10.1002/path.4515/abstract][][ACK1
  Promotes Gastric Cancer Epithelial-Mesenchymal Transition and
  Metastasis through AKT-POU2F1-ECD Signaling]\from[url22].
  {\bf {\em The Journal of Pathology}}. 2015, 236(2):175-185.
\item
  Z Guo, J Han, XY Yang, K Cao, K He, G Du, G Zeng, L Zhang, {\bf G Yu},
  Z Sun, QY He\high{*}, X Sun\high{*}.
  \useURL[url23][http://pubs.rsc.org/en/content/articlelanding/2015/mt/C4MT00276H][][Proteomic
  analysis on the copper resistance of {\em Streptococcus
  pneumonia}]\from[url23]. {\bf {\em Metallomics}}. 2015, 7(3):448-454.
\item
  XY Yang, L Zhang, J Liu, N Li, {\bf G Yu}, K Cao, J Han, G Zeng, Y
  Pan, X Sun\high{*}, QY He\high{*}.
  \useURL[url24][http://www.sciencedirect.com/science/article/pii/S1874391914005521][][Proteomic
  analysis on the antibacterial activity of a Ru(II) complex against
  {\em Strepococcus pneumonia}]\from[url24]. {\bf {\em Journal of
  Proteomics}}. 2015, 115:107-116.
\item
  N Wang\high{†}, J Zhang\high{†}, L Zhang, XY Yang, N Li, {\bf G Yu}, J
  Han, K Cao, Z Guo, X Sun\high{*}, QY He\high{*}.
  \useURL[url25][http://pubs.rsc.org/en/content/articlelanding/2014/mt/c4mt00027g][][Proteomic
  analysis of putative heme-binding proteins in {\em Streptococcus
  pyogenes}]\from[url25]. {\bf {\em Metallomics}}. 2014, 6(8):1451-1459.
\item
  H Sun\high{*}, J Weng, {\bf G Yu}, RH Massawe.
  \useURL[url26][http://www.plosone.org/article/info\%3Adoi\%2F10.1371\%2Fjournal.pone.0077090][][A
  DNA-Based Semantic Fusion Model for Remote Sensing Data]\from[url26].
  {\bf {\em PLoS One}}. 2013, 8(10):e77090.
\item
  GR Yan\high{†}, Z Tan\high{†}, Y Wang, ML Xu, {\bf G Yu}, Y
  Li\high{*}, QY He\high{*}.
  \useURL[url27][http://onlinelibrary.wiley.com/doi/10.1002/pmic.201300152/abstract][][Quantitative
  Proteomics Characterization on the Anti-tumor Effects of
  Isodexyelephantopin against Nasopharyngeal Carcinoma]\from[url27].
  {\bf {\em Proteomics}}. 2013, 13(21):3222-3232.
\item
  J Li, X Lu, Q Wu, {\bf G Yu}, Z Xu, L Qiu, Z Pei, Y Lin, J
  Pang\high{*}.
  \useURL[url28][http://www.eurekaselect.com/107734/article][][Design,
  SAR, angiogenic activities evaluation and pro-angiogenic mechanism of
  new marine cyclopeptide analogs]\from[url28]. {\bf {\em Current
  Medicinal Chemistry}}. 2013, 20(9):1183-1194.
\item
  Y Han, {\bf G Yu}, H Sarioglu, A Caballero-Martinez, F Schlott, M
  Ueffing, H Haase, C Peschel, AM Krackhardt\high{*}.
  \useURL[url29][http://www.sciencedirect.com/science/article/pii/S1874391912007567][][Proteomic
  investigation of the interactome of FMNL1 in hematopoietic cells
  unveils a role in calcium-dependent membrane plasticity]\from[url29].
  {\bf {\em Journal of Proteomics}}. 2013, 78:72-82.
\item
  Y Ma\high{†}, J Yang\high{†}, X Fan\high{†}, H Zhao, W Hu, Z Li,
  {\bf G Yu}, X Ding, J Wang, X Bo, X Zheng, Z Zhou\high{*}, S
  Wang\high{*}.
  \useURL[url30][http://onlinelibrary.wiley.com/doi/10.1111/j.1582-4934.2012.01572.x/abstract][][Cellular
  MicroRNA let-7c Inhibits M1 Protein Expression of the H1N1 Influenza A
  Virus in Infected Human Lung Epithelial Cells]\from[url30].
  {\bf {\em Journal of Cellular and Molecular Medicine}}. 2012,
  16(10):2539-2546.
\item
  GR Yan\high{†}, FY Zhou\high{†}, BL Dang, Y Zhang, {\bf G Yu}, X Liu,
  QY He\high{*}.
  \useURL[url31][http://onlinelibrary.wiley.com/doi/10.1002/pmic.201100652/abstract][][Genistein-induced
  mitotic arrest of gastric cancer cells by downregulating KIF20A, a
  proteomics study]\from[url31]. {\bf {\em Proteomics}}. 2012,
  12(14):2391-2399.
\item
  X Sun\high{†}, XY Yang\high{†}, XF Yin, {\bf G Yu}, CL Xiao, X He, QY
  He\high{*}.
  \useURL[url32][http://www.liebertonline.com/doi/abs/10.1089/omi.2010.0133][][Proteomic
  Analysis of Membrane Proteins from {\em Streptococcus pneumoniae} with
  Multiple Separation Methods plus High Accuracy Mass
  Spectrometry]\from[url32]. {\bf {\em OMICS: A Journal of Integrative
  Biology}}. 2011, 15(10):683-694.
\stopitemize

\subsection[book-chapters]{Book Chapters}

\startitemize[packed]
\item
  {\bf G Yu}, \quotation{Bioinformatics II}, in \quotation{Functional
  Protein Research}, 385-425, Qing-Yu He (Eds), {\bf {\em Science
  Press}}, 2012. (China's Twelfth Five-Year National Important Books
  Project, in Chinese)
\stopitemize

\stoptext
